Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2020-02-04 xrb/submit/paper.tex
Added new data for the 1000 Hz run
The flame speed dropped a bit - by about 10%. The true uncertainties on
the speeds should probably be a bit larger, but I am not certain how to
quantify them. Regardless, it is still nearly twice as fast as the
standard run.

\begin{deluxetable}{lc}
	\tablecaption{\label{table:flame_speeds_multid} Flame speeds measured in 2D calculations.}
	\tablehead{\colhead{run} & \colhead{$s_\mathrm{front}$ (km s$^{-1}$)}} 
	\startdata
	10/10 & $9.18 \pm 0.03$ \\
	5/5 & $4.00 \pm 0.01$ \\
	10/10-iso7 & $7.56 \pm 0.02$ \\
	10/10-lowres & $9.33 \pm 0.04$ \\
	10/10-1000 Hz & $18.6 \pm 0.16$ \\
	\enddata
	%
\end{deluxetable}

@@

All of the various approximations have the expected effects. The flame in the 5/5
boost run propagates at about half the speed of the 10/10 flame. This is consistent
with the 1D laminar flames, and is the behavior predicted by Eq.~\ref{eq:flame_scaling}. The
1000~Hz run goes 2 times faster than the 10/10 2000~Hz run, as expected from the
inverse relation between rotation rate and the ratio of burning front area to scale height \citep{cavecchi:2013}.
This confirms that the role of the Coriolis
force is to limit the rate of flame spreading by the anticipated geometrical/hydrodynamical
effect ($s_\mathrm{front} = s_L * L_R / H$). Reducing the resolution had minimal impact on
the flame speed -- the low resolution line is right on top of the fit for the standard run
in Figure \ref{fig:flame_speed}, with their slopes differing by only a few percent. Using a
smaller network also produces similar behavior to the standard run, although there is a small
reduction in speed owing to less energetic burning.

>>>>

\begin{deluxetable}{lc}
	\tablecaption{\label{table:flame_speeds_multid} Flame speeds measured in 2D calculations.}
	\tablehead{\colhead{run} & \colhead{$s_\mathrm{front}$ (km s$^{-1}$)}} 
	\startdata
	10/10 & $9.18 \pm 0.03$ \\
	5/5 & $4.00 \pm 0.01$ \\
	10/10-iso7 & $7.56 \pm 0.02$ \\
	10/10-lowres & $9.33 \pm 0.04$ \\
	10/10-1000 Hz & $16.5 \pm 0.21$ \\
	\enddata
	%
\end{deluxetable}

@@

All of the various approximations have the expected effects. The flame in the 5/5
boost run propagates at about half the speed of the 10/10 flame. This is consistent
with the 1D laminar flames, and is the behavior predicted by Eq.~\ref{eq:flame_scaling}. The
1000~Hz run goes nearly 2 times faster than the 10/10 2000~Hz run, as expected from the
inverse relation between rotation rate and the ratio of burning front area to scale height \citep{cavecchi:2013}.
This confirms that the role of the Coriolis
force is to limit the rate of flame spreading by the anticipated geometrical/hydrodynamical
effect ($s_\mathrm{front} = s_L * L_R / H$). Reducing the resolution had minimal impact on
the flame speed -- the low resolution line is right on top of the fit for the standard run
in Figure \ref{fig:flame_speed}, with their slopes differing by only a few percent. Using a
smaller network also produces similar behavior to the standard run, although there is a small
reduction in speed owing to less energetic burning.
